---
title: A kickass title

author: |
  | Author1^[Corresponding author: author@gmail.com], et al. 
  | $^1$ An affiliation 

abstract: |
  A sweet abstract

bibliography: references.bib
csl: american-journal-of-epidemiology.csl
link-citations: yes

output:
  bookdown::pdf_document2:
    includes:
      in_header: preamble.tex
    toc: False
fig_caption: yes

always_allow_html: yes
---

```{r setup, message=FALSE, warning=FALSE, include=FALSE}
pkgs <- c("bookdown", "knitr", "kableExtra", "tidyverse")
lapply(pkgs, require, character.only = TRUE)

knitr::opts_chunk$set(echo = FALSE, 
            warning = FALSE, 
            message = TRUE, 
            cache = FALSE, 
            dpi = 300 
            )

# Function for numbers in rmarkdown
comma <- function(x) format(x, digits = 2, big.mark = ",")
```

```{r call_source}
read_chunk("paper.R")
```

``` {r load-data, results="hide", message=FALSE}
```

``` {r study-data-setup, results="hide", message=FALSE}
```

``` {r readymade-plot-setup, results = "hide", message=FALSE}
```

``` {r other-plot-setup, results = "hide", message=FALSE}
```


\newpage

## Introduction {-#introduction}
Some intro and here is a reference test @Relton2010


\newpage

## Methods {-#methods}

### an-example-subheading {-#an-example-subheading}

Here is an equation for you nerds out there:

\begin{equation} 
  f\left(k\right) = \binom{n}{k} p^k\left(1-p\right)^{n-k}
  (\#eq:binom)
\end{equation} 

Well would you look at that sweet equation. Let's give it a reference: if you love a binomial distribution look at equation \@ref(eq:binom)

### Code availability {-#code-availability}
Code used to run the analyses is available here: https://github.com/thomasbattram/something

All analyses were completed using R (version __X__).

\newpage

## Results {-#results}

### study data example {-#study-data-example}

```{r study-data-tab, message=FALSE, results="asis"}
```

__Table \@ref(tab:study-data-tab)__

### another subheading {-#another-subheading}

Well wouldn't you look below it's __Figure \@ref(fig:a-figure-example)__

(ref:fig-caption-example) This is an example text reference for a figure caption. 

```{r a-figure-example, message=FALSE, results="asis", fig.cap='(ref:fig-caption-example)'}
```

And look at this, one more figure!!! See __Figure \@ref(fig:another-plot)__

(ref:fig-caption-example2) This is an example text reference for a figure caption. 

```{r another-plot, message=FALSE, results="asis", fig.cap='(ref:fig-caption-example2)'}
```

Let's link to my github page because I can [Tom's github](https://github.com/thomasbattram).

Haven't figured out how to link to __Supplementary figures__ yet.

\newpage

## Discussion {-#discussion}

### A discussion subheading {-#a-discussion-subheading}

### Limitations {-#limitations}

## Conclusion {-#conclusion}
Overall this paper is the best and should be accepted in Nature, Science, NEJM and JAMA all at the same time.

\newpage

## References {-#references}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
